\documentclass[hidelinks]{report}

% load packages
\usepackage[english]{babel}
\usepackage{datetime}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{fontspec}
\usepackage[a4paper, left=15mm, top=15mm, right=15mm, bottom=15mm]{geometry}
\usepackage{hanging}
\usepackage{hyperref}
\usepackage{academicons}
\usepackage[fontsize=9pt]{scrextend}
\usepackage{setspace}
\usepackage{ulem}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[utf8]{inputenc}
\usepackage{marvosym}

% setup document options
\setmainfont[BoldFont=Montserrat-Bold, ItalicFont=Montserrat-Italic]{Montserrat}
\setmonofont{Ubuntu Mono}
\doublespacing
\setlength\parindent{0pt}
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define colors Egypt palette
% \definecolor{blue}{HTML}{007aa1}
% \definecolor{red}{HTML}{e04e25}
% \definecolor{green}{HTML}{40b282}
% \definecolor{yellow}{HTML}{fdb252}
\definecolor{blue}{HTML}{007BA5}
\definecolor{red}{HTML}{F24000}
\definecolor{green}{HTML}{0BB67D}
\definecolor{yellow}{HTML}{FFAF38}

% define other colors
\definecolor{orc}{HTML}{a6ce39}
\definecolor{grey}{HTML}{5d5d5d}

% footer 
\pagestyle{fancy}

\renewcommand{\headrulewidth}{0pt}

\fancyfoot[L]{{\scriptsize \textcolor{blue}{\monthyeardate\today}}}
\fancyfoot[C]{{\scriptsize \textcolor{blue}{Maximilian H.K. Hesselbarth - Curriculum Vitae}}}
\fancyfoot[R]{\scriptsize \textcolor{blue}{{\thepage}}}

% begin document
\begin{document}

% Header
%------%

\begin{center}

\huge Maximilian H.K. Hesselbarth \small{\textit{(he/him)}}

\textcolor{red}{\small{\textbf{Research Scholar}}}

\textcolor{blue}{\small{Biodiversity, Ecology, and Conservation Group}}

\textcolor{blue}{\small{International Institute for Applied Systems Analysis (IIASA)}}

\small{
	\faEnvelope \hspace{0.1em} \href{mailto:mhk.hesselbarth@gmail.com}{mhk.hesselbarth@gmail.com} \hspace{1em}
	\faHome \href{https://www.maxhesselbarth.com}{\hspace{0.1em} www.maxhesselbarth.com} \hspace{1em}
	\faGithub \href{https://github.com/mhesselbarth}{\hspace{0.1em} mhesselbarth} \hspace{1em}
	\textcolor{orc}{\aiOrcid} \href{https://orcid.org/0000-0003-1125-9918}{\hspace{0.1em} 0000-0003-1125-9918}
}

\end{center}

% \vspace{1.0em}
 
% Job appointments
%----------------%

\section*{\textcolor{red}{Professional} Appointments \sout{\hfill}}

International Institute for Applied Systems Analysis (IIASA)
\hfill
\textcolor{green}{Laxenburg, Austria}

\textcolor{grey}{\footnotesize{Research Scholar; Biodiversity, Ecology, and Conservation Group}}
\hfill
\textcolor{grey}{\textit{2023/02/15 - ongoing}}

University of Michigan
\hfill
\textcolor{green}{Ann Arbor, USA}

\textcolor{grey}{\footnotesize{Postdoctoral Fellow; Coastal Ecology and Conservation Lab}}
\hfill
\textcolor{grey}{\textit{2020/08/01 - 2022/12/31}}

% Education
%---------%

\section*{\textcolor{red}{Education} \sout{\hfill}}

% PhD
University of Goettingen
\hfill
\textcolor{green}{Goettingen, Germany}

\textcolor{grey}{\footnotesize{Dr. rer. nat; Department of Ecosystem Modelling}}
\hfill
\textcolor{grey}{\textit{2016/10/01 - 2020/04/06}}

% M.Sc.
University of Goettingen
\hfill
\textcolor{green}{Goettingen, Germany}

\textcolor{grey}{\footnotesize{Master of Sciences; Ecosystem Analysis and Modelling}}
\hfill
\textcolor{grey}{\textit{2014/10/01 - 2016/11/15}}

% B.Sc.
University of Applied Sciences and Arts
\hfill
\textcolor{green}{Goettingen, Germany}

\textcolor{grey}{\footnotesize{Bachelor of Sciences; Forestry}}
\hfill
\textcolor{grey}{\textit{2011/10/01 - 2014/07/07}}

% Internships
%-----------%

\section*{\textcolor{red}{Internships} / Research visits \sout{\hfill}}

% Iowa
Iowa State University
\hfill
\textcolor{green}{Ames, USA}

\textcolor{grey}{\footnotesize{Department of Ecology, Evolution and Organismal Biology}}
\hfill
\textcolor{grey}{\textit{2017/10/18 - 2017/12/21}}

% Pietermaritzburg
University of KwaZulu-Natal
\hfill
\textcolor{green}{Pietermaritzburg, South Africa}

\textcolor{grey}{\footnotesize{School of Life Sciences}}
\hfill
\textcolor{grey}{\textit{2016/03/07 - 2016/08/01}}

% Potch
North-West University
\hfill
\textcolor{green}{Potchefstroom, South Africa}

\textcolor{grey}{\footnotesize{Land Degradation and Restoration Ecology}}
\hfill
\textcolor{grey}{\textit{2016/03/07 - 2016/08/01}}

% Versuchsanstalt
Northwest German Forestry Research Institute
\hfill
\textcolor{green}{Goettingen, Germany}

\textcolor{grey}{\footnotesize{Department of Growth Modeling}}
\hfill
\textcolor{grey}{\textit{2015/09/01 - 2015/10/01}}

% Malawi
SilvaTerra Ltd.
\hfill
\textcolor{green}{Lilongwe, Malawi}

\textcolor{grey}{\footnotesize{Forest Consulting and Research}}
\hfill
\textcolor{grey}{\textit{2013/11/04 - 2014/03/30}}

% Battens
Wise Batten Inc.
\hfill
\textcolor{green}{Estill, USA}

\textcolor{grey}{\footnotesize{Forestry Services and Wildlife Management}}
\hfill
\textcolor{grey}{\textit{2011/06/02 - 2011/08/01}}

% Forstamt Heuberg
State Forestry Department Heuberg
\hfill
\textcolor{green}{Messtetten, Germany}

\textcolor{grey}{\footnotesize{Forest Managment}}
\hfill
\textcolor{grey}{\textit{2010/08/02 - 2010/08/27}}

% Forstamt Heuberg
State Forestry Department Heuberg
\hfill
\textcolor{green}{Messtetten, Germany}

\textcolor{grey}{\footnotesize{Forest Managment}}
\hfill
\textcolor{grey}{\textit{2009/08/31 - 2009/09/11}}


% Conferences
%-----------%

\section*{\textcolor{red}{Conferences} / Workshops \footnotesize{(attended)} \sout{\hfill}}


% GFO
52nd Annual Meeting of the Ecological Society of Germany, Austria and Switzerland
\hfill
\textcolor{green}{Leipzig, Germany}

\hfill
\textcolor{grey}{\textit{2023/09/12 - 2023/09/16}}

% IALE
World Congress International Association of Landscape Ecology
\hfill
\textcolor{green}{Milano, Italy}

\hfill
\textcolor{grey}{\textit{2019/07/01 - 2019/07/05}}

% GFO
48th Annual Meeting of the Ecological Society of Germany, Austria and Switzerland
\hfill
\textcolor{green}{Vienna, Austria}

\hfill
\textcolor{grey}{\textit{2018/09/10 - 2018/09/14}}

% inlabru workshop
Spatial Modelling \textit{inlabru}
\hfill
\textcolor{green}{St. Andrews, UK}

\hfill
\textcolor{grey}{\textit{2018/03/26 - 2018/03/30}}

% Machine learning
Deep Learning with \textit{Keras} and \textit{TensorFlow}
\hfill
\textcolor{green}{Solingen, Germany}

\hfill
\textcolor{grey}{\textit{2018/01/18 - 2018/01/19}}

% Yomos
Young Modellers in Ecology
\hfill
\textcolor{green}{Freiburg, Germany}

\hfill
\textcolor{grey}{\textit{2017/04/29 - 2017/05/05}}

% PR Stats
Advances in Spatial Analysis of Multivariate Ecological Data
\hfill
\textcolor{green}{Port Talbot, UK}

\hfill
\textcolor{grey}{\textit{2017/04/02 - 2017/04/07}}

% Cyprus
Fire Protection and Management
\hfill
\textcolor{green}{Prodromos, Cyprus}

\hfill
\textcolor{grey}{\textit{2013/09/07 - 2013/09/22}}

% Publications
%-----------%

\section*{\textcolor{red}{Publications} \sout{\hfill}}

\textcolor{grey}{\footnotesize{Copies of all publications and talks can be found on my homepage.}}
\textcolor{green}{\footnotesize{\Cross \hspace{0.1em} Authors contributed equally}}

\subsection*{Articles}

\begin{hangparas}{7.5mm}{1}
	
\textcolor{yellow}{Hesselbarth, M.H.K.} \textcolor{green}{\Cross}, Allgeier, J.E. \textcolor{green}{\Cross} (In press). \textit{High fish biomass and low nutrient enrichment synergistically enhance stability in a seagrass meta-ecosystem}. Conservation Letters.	

Munsterman, K.S., \textcolor{yellow}{Hesselbarth, M.H.K.}, Allgeier, J.E. (In press). \textit{Smaller and bolder fish enhance ecosystem-scale primary production around artificial reefs in seagrass beds}. Ecological Applications. % \url{https://doi.org/10.1002/eap.3055} % 
		
Nowosad, J., \textcolor{yellow}{Hesselbarth, M.H.K.} (2024). \textit{The landscapemetrics and motif packages for measuring landscape patterns and processes}. arxiv, stat.ME. \url{https://doi.org/10.48550/arxiv.2405.06559}

\textcolor{yellow}{Hesselbarth, M.H.K.}, Wiegand, K. (2024). \textit{A simulation study comparing common methods for analyzing species-habitat associations of plants.} Journal of Vegetation Science 35, e13243. \url{https://doi.org/10.1111/jvs.13243}
	
Shayka, B.F., \textcolor{yellow}{Hesselbarth, M.H.K.}, Schill, S.R., Currie, W.S., Allgeier, J.E. (2023). \textit{The natural capital of seagrass beds in the Caribbean: evaluating their ecosystem services and blue carbon trade potential}. Biology Letters 19:20230075. \url{https://doi.org/10.1098/rsbl.2023.0075}
	
Rubio-Camacho, E.A., \textcolor{yellow}{Hesselbarth, M.H.K.}, Flores-Garnica, J.-G., Acosta-Mireles, M. (2023). \textit{Tree mortality in mature temperate forests of central Mexico: A spatial approach}. European Journal of Forest Research 142, 565–577. \url{https://doi.org/10.1007/s10342-023-01542-3}

Simpkins, C.E., Hanss, S., Spangenberg, M.C., Salecker, J., \textcolor{yellow}{Hesselbarth, M.H.K.}, Wiegand, K. (2022). \textit{spectre: An R package to estimate spatially-explicit community composition using sparse data}. Ecography 2022 (12), e06272 \url{https://doi.org/10.1111/ecog.06272}

Esquivel, K.E. \textcolor{green}{\Cross}, \textcolor{yellow}{Hesselbarth, M.H.K.} \textcolor{green}{\Cross}, Allgeier, J.E. (2022). \textit{Mechanistic support for increased primary production around artificial reefs}. Ecological Applications 32 (6), e2617. \url{https://doi.org/10.1002/eap.2617}

\textcolor{yellow}{Hesselbarth, M.H.K.} (2021). \textit{shar: An R package to analyze species-habitat associations using point pattern analysis}. Journal of Open Source Software 6 (68), 3811. \url{https://doi.org/10.21105/joss.03811}

\textcolor{yellow}{Hesselbarth, M.H.K.}, Nowosad, J., Signer, J., Graham, L.J. (2021). \textit{Open-source tools in R for landscape ecology}. Current Landscape Ecology Reports 6 (3), 97-111. \url{https://doi.org/10.1007/s40823-021-00067-y}

Borthwick, R. \textcolor{green}{\Cross}, de Flamingh, A. \textcolor{green}{\Cross}, \textcolor{yellow}{Hesselbarth, M.H.K.} \textcolor{green}{\Cross}, Parandhaman, A. \textcolor{green}{\Cross}, Wagner, H.H., Abdel Moniem, H.E.M. (2020). \textit{Alternative Quantifications of Landscape Complementation to Model Gene Flow in Banded Longhorn Beetles [Typocerus v. velutinus (Olivier)]}. Frontiers in Genetics 11, 307. \url{https://doi.org/10.3389/fgene.2020.00307}

\textcolor{yellow}{Hesselbarth, M.H.K.} (2020). \textit{Analysing and modelling spatial patterns to infer the influence of environmental heterogeneity using point pattern analysis, individual-based simulation modelling and landscape metrics} (Dissertation). University of Goettingen, Goettingen, Germany. \url{http://dx.doi.org/10.53846/goediss-7959}

\textcolor{yellow}{Hesselbarth, M.H.K.}, Sciaini, M., With, K.A., Wiegand, K., Nowosad, J. (2019). \textit{landscapemetrics: An open-source R tool to calculate landscape metrics}. Ecography 42 (10), 1648-1657. \url{https://doi.org/10.1111/ecog.04617}

\textcolor{yellow}{Hesselbarth, M.H.K.}, Wiegand, K., Dreber, N., Kellner, K., Esser, D., Tsvuura, Z. (2018). \textit{Density-dependent spatial patterning of woody plants differs between a semi-arid and a mesic savanna in South Africa}. Journal of Arid Environments 157, 103-112. \url{https://doi.org/10.1016/j.jaridenv.2018.06.002}

\end{hangparas}

\subsection*{Presentations}

\begin{hangparas}{7.5mm}{1}

\textcolor{yellow}{Hesselbarth, M.H.K.}, Jung, M., Visconti, P. (2024). \textit{Forest biodiversity under changing climate and forest structure}. 2nd ForestNavigator Stakeholder Workshop. Brussels (Belgium).
	
\textcolor{yellow}{Hesselbarth, M.H.K.}, Jung, M., Visconti, P. (2023). \textit{Evaluating the impact of European forest management on forest-related species using iSDMs}. 52nd Annual Meeting of the Ecological Society of Germany, Austria and Switzerland. Leipzig (Germany).
	
\textcolor{yellow}{Hesselbarth, M.H.K.}, Jung, M., Visconti, P. (2023). \textit{Biodiversity indicators and species distribution modeling}. 1st ForestNavigator Stakeholder Workshop. Laxenburg (Austria).

\textcolor{yellow}{Hesselbarth, M.H.K.}, Munsterman, K.S. (2022). \textit{Advanced R Workshop}. Ecology and Evolutionary Biology Department, University of Michigan. Ann Arbor (USA). Workshop.

\textcolor{yellow}{Hesselbarth, M.H.K.} (2022). \textit{Artificial reefs to promote primary production in tropical seagrass ecosystems: A simulation study using individual-based modelling}. Ecology and Evolutionary Biology Department Seminar, University of Michigan. Ann Arbor (USA). Talk.

\textcolor{yellow}{Hesselbarth, M.H.K.} (2022). \textit{Introduction to R Workshop}. Ecology and Evolutionary Biology Department, University of Michigan. Ann Arbor (USA). Workshop.

\textcolor{yellow}{Hesselbarth, M.H.K.} (2021). \textit{Spatial patterns in ecology and what we (hopefully) can learn from them}. Ecology and Evolutionary Biology Department Seminar, University of Michigan. Ann Arbor (USA). Talk.

Nowosad, J., \textcolor{yellow}{Hesselbarth, M.H.K.} (2020). \textit{Introduction to landscape ecology with R}. Annual Meeting International Association of Landscape Ecology North America. Toronto (Canada). Workshop.

\textcolor{yellow}{Hesselbarth, M.H.K.}, Sciaini, M., Nowosad, J., Hanss, S. (2019). \textit{landscapemetrics: Introducing a new R tool to characterize landscapes}. 10th World Congress International Association of Landscape Ecology. Milano (Italy). Conference poster.

\textcolor{yellow}{Hesselbarth, M.H.K.}, Wiegand K. (2018). \textit{A simulation study comparing methods to analyze species-habitat associations of forest trees}. 48th Annual Meeting of the Ecological Society of Germany, Austria and Switzerland. Vienna (Austria). Conference poster.

\end{hangparas}

% Software 
%--------%

\section*{\textcolor{red}{Software} \sout{\hfill}}

% arrR
\texttt{arrR} \textcolor{grey}{Simulating artificial reefs in R}
\hfill
\footnotesize{\textcolor{green}{\href{https://allgeier-lab.github.io/arrR/}{https://allgeier-lab.github.io/arrR/}}}

% landscapemetrics
\texttt{landscapemetrics} \textcolor{grey}{Landscape Metrics for Categorical Map Patterns.}
\hfill
\footnotesize{\textcolor{green}{\href{https://r-spatialecology.github.io/landscapemetrics/}{https://r-spatialecology.github.io/landscapemetrics/}}}

% shar
\texttt{shar} \textcolor{grey}{Species-Habitat Associations.}
\hfill
\footnotesize{\textcolor{green}{\href{https://r-sptialecology.github.io/shar/}{https://r-sptialecology.github.io/shar/}}}

% onpoint
\texttt{onpoint} \textcolor{grey}{Helper Functions related to Point Pattern Analysis.}
\hfill
\footnotesize{\textcolor{green}{\href{https://r-spatialecology.github.io/onpoint/}{https://r-spatialecology.github.io/onpoint/}}}

% \newpage

% Peer reviewer 
%--------%

\section*{\textcolor{red}{Peer reviewer} for scientific journals \sout{\hfill}}

Ecological Indicators;
Global Ecology and Biogeography;
Journal of Animal Ecology;
Journal of Open Source Software;
Journal of Tropical Ecology;
Journal of Vegetation Science;
Landscape Ecology;
Methods in Ecology and Evolution;
PeerJ;
Perspective in Plant Ecology, Evolution and Systematics;
Plant and Soil;
Plant Ecology;
PLOS One;
Restoration Ecology;
Scientific Reports;
Synthesis Centre for Biodiversity Sciences;
Web Ecology

% \newpage

% Skills
%--------%

\section*{\textcolor{red}{Skills} \sout{\hfill}}

Languages: German (native), English (fluent)

\begin{center}
	\begin{tabular}{l l l l}
		
		R: \textcolor{green}{\faCircle \faCircle \faCircle \faCircle \faCircle} & 
		C++: \textcolor{green}{\faCircle \faCircle \faCircle \faCircleO \faCircleO} & 
		NetLogo: \textcolor{green}{\faCircle \faCircle \faCircleO \faCircleO \faCircleO} &
		HTML, CSS: \textcolor{green}{\faCircle \faCircleO \faCircleO \faCircleO \faCircleO} \\
	
		SQL/SQLite: \textcolor{green}{\faCircle \faCircleO \faCircleO \faCircleO \faCircleO} &
		LaTeX: \textcolor{green}{\faCircle \faCircle \faCircle \faCircleO \faCircleO} &
		git: \textcolor{green}{\faCircle \faCircle \faCircle \faCircleO \faCircleO} &
		QGIS: \textcolor{green}{\faCircle \faCircle \faCircleO \faCircleO \faCircleO} \\

	\end{tabular}
\end{center}

\end{document}
